---
title: "p8105_hw5_ob2305"
author: "Olya Besedina"
data: "11/04/2019"
output: github_document
---
  
```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(viridis)

knitr::opts_chunk$set(
 	echo = TRUE,
 	warning = FALSE,
 	fig.width = 8, 
   fig.height = 6,
   out.width = "90%"
 )

options(
   ggplot2.continuous.colour = "viridis",
   ggplot2.continuous.fill = "viridis"
 )

 scale_colour_discrete = scale_colour_viridis_d
 scale_fill_discrete = scale_fill_viridis_d

 theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

# Problem 1

Count missing values in the df

```{r}
skimr::skim(iris_with_missing)
```

```{r}
iris_with_missing = iris_with_missing %>% janitor::clean_names()

# function for num and char
my_function = function(x) {
  
  if(is.numeric(x)) {
    replace_na(x, mean(x, na.rm = TRUE))
  } else if(is.character(x)) {
    replace_na(x, "virginica")
  }
}
new_iris = map_df(iris_with_missing,my_function)

# check missing values in mapped data frame
sum_na = sum(is.na(new_iris))
names = distinct(new_iris,species)

# in line 
# The `r new_iris` data frame has `r sum_na` missing values. In character variables missing values were replaced withthe mean value of that variable and in character variable they were replaced with "virginica". Character value in the new data frame has three distinct values `r names`.
```



# Problem 2

* Read in data for each subject 
```{r}
# Read the files

read_plus <- function(x) {
    read_csv(x) %>% 
        mutate(filename = x)
}

trial =
    list.files(path = "./data/", 
               pattern = "*.csv",
               full.names = TRUE)

trial_df = map_df(trial, read_plus)
```

* Tidy the result

```{r, tidy results}
trial_tidy =
  trial_df %>%
  pivot_longer(
     -filename,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>% 
  mutate(
    filename = str_replace(filename, "./data//", ""),
    filename = str_replace(filename, ".csv", "")
  ) %>%  
  separate(filename, into = c("arm", "subject_id"), sep = "\\_")
 
trial_nest = 
  nest(trial_tidy, data = week:value) %>% 
  head()
```

* Spaghetti plot 

```{r, spaghetti plot}
trial_tidy %>% 
  ggplot(aes(x = week, y = value, color = subject_id, group = subject_id)) +
  geom_line() +
  facet_grid(~arm)+
  labs(
    title = "Change of values over 8 weeks for each participant"
  )
```

The plot above depicts change of values over the 8 weeks of trial for each participant in control and experimental arms. It can be seen from the plot that participants in experimental arm had an upward trend of values, in contrast to participants in the control arm.


# Problem 3

```{r}

sim_regression = function(beta0 = 2, beta1 = 0) {
  
  data = tibble(
    x = rnorm(30, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(30, 0, sqrt(50))
  )
  
  ls_fit = lm(y ~ x, data = data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}

```

Generate 10000 datasets from the model

```{r}
output = rerun(10000, sim_regression()) %>% 
  bind_rows()

```







